%%
The Police Forces have an important role in the new strategy developed in order to overcome the problem of map exploration faced in RoboCup 2011. Each one is given the task of performing the surveillance of a specific partition of the map. Other teams such as MRL, HfutEngineRescue, IAMRescue, and RMAS\_ArtSapience have already reported the use of mapping partitioning and we think that it will help us too. Hence, our intents in partitioning the map were (i) to be able to better explore the map and identify faster possible tasks to act upon, and (ii) reduce the number of entities that each Police Force has to check fastening the exploration process.

Besides, since Fire Brigades need to get to refuges to refill their water tank and Ambulance Teams need to have fast ways to reach the refuge when transporting civilians, clearing paths to refuges is considered crucial in our strategy. Therefore, in order to make refuges accessible to the other kinds of agents, the first task of the Police Forces are to move to the closest refuge located in its sector, if there is any, clearing the blockades in the path.

Once it reaches the refuge, the Police Force starts patrolling its sector by visiting each road and building contained in it. During such activity, it may find new blockades or receive blockades information from other agents, requiring it to choose a blockade to act upon: for this, it first rules out the blockades that have other agent acting upon, since there is no advantage of more than one Police Force acting in the same blockade, and calculates the payoff of the remaining blockades. The payoff calculus (Eq. \ref{eq:policeForce}) takes into account the blockade repair cost and its distance, giving higher payoffs to blockades with small repair cost and that are closer to the agent.
%%
\begin{equation}
\label{eq:policeForce}
%%
\frac{1}{repairCost} * \frac{1}{\sqrt{distance}}
%%
\end{equation}
%%

In order to clear more roads and cover a broader area, the Police Force clears the blockades in a way it can transpose it. In some cases, this does not require the complete clearing of the blockade, which saves time improving the overall Police Force results.
%%
